Guide for manual trajectory inference

### 2018-07-09 scripts/manual_ti/guide.Rmd

datasets_control <- read_rds(derived_file("datasets.rds", "1-datasets/control"))
space <- datasets_control %>% filter(id == "control_bifurcating") %>% pull(space) %>% first()
```

>>>>

datasets_control <- read_rds(derived_file("datasets.rds", "01-datasets/control"))
space <- datasets_control %>% filter(id == "control_bifurcating") %>% pull(space) %>% first()
```
